---
title: "Homework 2"
author: "Ben Chu"
date: "February 26, 2018"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(psych)
library(purrr)
library(stats)
library(DescTools)
library(car)
library(lm.beta)
library(lmtest)
library(lmSupport)
par(mfrow = c(2,2))
options(warn=-1)
```
###Loading the data
```{r}
load("C:/Users/Branly Mclanbry/Downloads/grants.RData")
hw2 <- grants %>% janitor::clean_names()
```
###Some functions
```{r}
pphehe <- function(x,var) {
 (qqnorm(x, main = var))
 (qqline(x))
}
denss <- function(x,var) {
  plot(density(x), main = var)
}

skurt <-function(x,var) {
  skew.1 <- round(DescTools::Skew(x, method = 2, conf.level = .99),2)
  kurt.1 <- round(DescTools::Kurt(x, method = 2, conf.level = .99),2)
  print(list(var,skew.1,kurt.1))
}

transformerbots <- function(x,var){
  print(var)
  print("squareroot")
  squareroot <- (x+1)^.5
  print(round(DescTools::Skew(squareroot,na.rm=TRUE, method=2,conf.level=.99),2))
  squareroot <- (x+1)^.5
  print(round(DescTools::Kurt(squareroot,na.rm=TRUE, method=2,conf.level=.99),2))
  print("log")
  log <- log10(x+1)
  print(round(DescTools::Skew(log,na.rm=TRUE, method=2,conf.level=.99),2))
  log <- log10(x+1)
  print(round(DescTools::Kurt(log,na.rm=TRUE, method=2,conf.level=.99),2))
   print("inverse")
  inverse <- 1/(x+1)
  print(round(DescTools::Skew(inverse,na.rm=TRUE, method=2,conf.level=.99),2))
  inverse <- 1/(x+1)
  print(round(DescTools::Kurt(inverse,na.rm=TRUE, method=2,conf.level=.99),2))
}

varlist <- list(hw2$submit,hw2$quality,hw2$univers,hw2$money)
names <- names(hw2)
```
#Question 1
```{r warnings = FALSE}
walk2(varlist,names,pphehe)
walk2(varlist,names,skurt)
walk2(varlist,names,denss)
varlist.1 <- list(hw2$univers,hw2$money)
names.1 <- names(hw2[3:4])
walk2(varlist.1,names.1,transformerbots)
```
Analysis suggests that money and university employer are positively skewed while quality and submissions are normally distributed.  
The most effective transformation for university and money is the log. 
```{r}
hw2 <- hw2 %>%
  mutate(univers_log = log10(univers+1),
         money_log = log(money+1))
```
#Question 1b
```{r}
hw2.mod <- lm(money_log ~ univers_log + quality + submit, dat = hw2)
summary(hw2.mod)
lm.beta(hw2.mod)
modelEffectSizes(hw2.mod)
```

#Question 1c
```{r}
plot(hw2.mod)
```

#Question 1d
```{r}
hw2.mod.2 <- lm(money ~ univers + quality + submit, dat = hw2)
summary(hw2.mod.2)
lm.beta(hw2.mod.2)
modelEffectSizes(hw2.mod.2)
```

#Question 1e
```{r}
n <- 50
hat <- hatvalues(hw2.mod)
mahun<-((n-1)*(hat))-1
tail(sort(mahun),10)
1-pchisq(16.76, df = 3)
```
```{r}
n <- 50
hat <- hatvalues(hw2.mod.2)
mahun<-((n-1)*(hat))-1
tail(sort(mahun),10)
1-pchisq(16.827, df = 3)
```

#Question 1f
vif(hw2.mod)
1/vif(hw2.mod)
vif(hw2.mod.2)
1/vif(hw2.mod.2)

#Question 1g
APA stuff, gotta do the write up.

#Question 1h
```{r}
lmtest::bptest(hw2.mod, varformula = ~ fitted.values(hw2.mod), studentize = FALSE)
```

#Question 1i 

#Question 1j
```{r}
lmtest::bptest(hw2.mod.2, varformula = ~ fitted.values(hw2.mod.2), studentize = FALSE)
```
#Question 1k
```{r}
library(MBESS)
ci.R2(R2=.30,N=50,K=3,conf.level =.95)
ci.R2(R2=.32,N=50,K=3,conf.level =.95)
```