---
title: "Lab 7"
author: "Ben Chu"
date: "April 23, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(psych)
load("C:/Users/Branly Mclanbry/Downloads/world95_lab7.RData")
```

```{r}
l7.2 <- world95_lab7

comp.l7 <- l7.2 %>%
  select(lifeexpf,lifeexpm,birth_rt,death_rt,pop_incr)
```
#lab 1a
There will probably be about 2 components, when I run a simple scree plot, it mostly shows 2 variables.
```{r}
scree(comp.l7)
```

#lab 1a+2c
2 factors is confirmed by the test of hypothesis and the ss loadings?
```{r}
comp.fn <- principal(comp.l7,nfactors = 2, rotate = "varimax")
fa.sort(comp.fn)
```
#lab 1f
Eigenvalues are a measure of explained variance, so a eigenvalue of 1 divided by 2 factors is about 50% explained variance. Which is fairly high.
```{r}
comp.fa <- fa(comp.l7,nfactors = 2, rotate="varimax",fm = "pa")
fa.sort(comp.fa)
```
#lab 2
Values changed, but i'm not entirely sure what's supposed to be whacky.But the items are not correlated so we see low eigenvalues?
```{r}
comp.ob <- fa(comp.l7, nfactors = 2, rotate = "oblimin", fm = "pa")
fa.sort(comp.ob)
```

#lab 3
The heywood case is when final communality exceeds one which is basically overestimated explained variance, or there is negative variance. Basically, some items are overly weighted.

#lab4
```{r}
load("C:/Users/Branly Mclanbry/Downloads/lab7cfa.RData")
l7 <- lab7cfa
cf_model <- "
  ag =~ 185+188+190+191+192
  co =~ 166+174+184+210+214
  ex =~ 178+198+201+208+216
  ne =~ 154 +160+163+164+171
  op =~ 165+175+179+197+203
"
library(lavaan)  
fit <- cfa(cf_model, data = l7, mimic = "MPLUS")
summary(fit,fit.measures = TRUE, standardized = TRUE)
```