---
title: "Lab Number One"
author: "Ben Chu"
date: "January 23, 2018"
output: html_document
---
```{r warning = FALSE, message = FALSE}
library(tidyverse)
```
#cleaning the data
```{r warning = FALSE}
uncleanlab1 <- read.csv("C:/Users/Branly Mclanbry/Downloads/lab1.csv")
lab1 <- uncleanlab1 %>%
  mutate(
    race = case_when(
      qa == 1 ~ "white",
      qa == 2 ~ "african-american",
      qa == 3 ~ "hispanic/latino",
      qa == 4 ~ "asian",
      qa == 5 ~ "native american",
      qa == 6 ~ "other"),
    support = (q1a + q1b +q1c))
```

###1a
These two are not statistically correlated with each other. *R*^2^ = .0007, *F*(1,76) = 0.06, *p* = .81

```{r}
regdat<-lm(support~qb,lab1)
summary(regdat)
cor.test(lab1$support,lab1$qb)
```

###1b
```{r}
newage = data.frame(qb=21)
predict(regdat,newage)
```

###1c
```{r}
plot(lab1$support,lab1$qb)
abline(lm(lab1$qb~lab1$support),col = "red")
```

#2a
These two are statistically correlated with each other. *R*^2^ = .31, *F*(1,76) = 34.3, *p* < .001
```{r}
beldat <-lm(support~q3,lab1)
summary(beldat)
cor.test(lab1$support,lab1$q3)
```
###2b
```{r}
newbel <- data.frame(q3=7)
predict(beldat,newbel)
```
###2c
```{r}
plot(lab1$support,lab1$q3)
abline(lm(lab1$q3~lab1$support))
```

###3a
These two are statistically correlated with each other. *R*^2^ = .06, *F*(1,76) = 5.13, *p* < .05
```{r}
knowdat <-lm(support~q2,lab1)
summary(knowdat)
cor.test(lab1$support,lab1$q2)
```
###3b
```{r}
newknow <- data.frame(q2=1)
predict(knowdat,newknow)
```
###3c
```{r}
plot(lab1$support,lab1$q2)
abline(lm(lab1$q2~lab1$support))
```

###4 

```{r}
library(stats)
cor.test(lab1$support,lab1$qb)
cor.test(lab1$support,lab1$q3)
cor.test(lab1$support,lab1$q2)
```
Appears to me that personal benefit is the strongest correlation, because the correlation is the largest.

###5 

I do not think it is a good analysis because ethnicity is a factors instead of numeric. Continuous variables are necessry for correlations.

###6

Restriction of range occurs with continuous variables that are not acurately/completely represented. I imagine that age may cause a problem regarding restriction of range. The dataset has a small range with all the 20 year olds.

