---
title: "Lab 3"
author: "Ben Chu"
date: "February 6, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(psych)
library(purrr)
library(stats)
library(DescTools)
library(car)
```
### Loading data and packages.
```{r}
load("C:/Users/Branly Mclanbry/Downloads/lab3.RData")
lab3 <- lab3 %>% janitor::clean_names()
```
##Q1
It appears that all variables are positively skewed. This is apparent in the 99% confidence intervals because 0 is no within the range. Similarly, kurtosis was an issue for all variables excelt mental health. 
###Descriptive statistics
```{r echo = FALSE, warning = FALSE}
describe(lab3)
```

###Functions for plots
```{r echo = FALSE}
pphehe <- function(x,var) {
 (qqnorm(x, main = var))
 (qqline(x))
}
denss <- function(x,var) {
  plot(density(x), main = var)
}
p_list <- list(lab3$timedrs, lab3$phyheal, lab3$menheal, lab3$stress)
names <- names(lab3[2:5])
```
###QQ Plots
```{r}
walk2(p_list,names,pphehe)
```

###Density Plots
```{r}
walk2(p_list,names,denss)
```


##Function for Skew and Kurtosis
```{r message=FALSE, warning=FALSE}
skurt <-function(x,var) {
  skew.1 <- round(DescTools::Skew(x, method = 2, conf.level = .99),2)
  print(var)
  kurt.1 <- round(DescTools::Kurt(x, method = 2, conf.level = .99),2)
  print(list(skew.1,kurt.1))
}
```
###Skew and Kurt for all variables
```{r message=FALSE, warning=FALSE}
walk2(p_list,names,skurt)
```

##Function for transofmrations
```{r}
transform <- function(x,var){
  print(var)
  print("squareroot")
  squareroot <- (x+1)^.5
  print(round(DescTools::Skew(squareroot,na.rm=TRUE, method=2,conf.level=.99),2))
  print("log")
  log <- log10(x+1)
  print(round(DescTools::Skew(log,na.rm=TRUE, method=2,conf.level=.99),2))
  print("inverse")
  inverse <- 1/(x+1)
  print(round(DescTools::Skew(inverse,na.rm=TRUE, method=2,conf.level=.99),2))
    print(var)
  print("squareroot")
  squareroot <- (x+1)^.5
  print(round(DescTools::Kurt(squareroot,na.rm=TRUE, method=2,conf.level=.99),2))
  print("log")
  log <- log10(x+1)
  print(round(DescTools::Kurt(log,na.rm=TRUE, method=2,conf.level=.99),2))
  print("inverse")
  inverse <- 1/(x+1)
  print(round(DescTools::Kurt(inverse,na.rm=TRUE, method=2,conf.level=.99),2))
}
```
##Q2
###Transformations
```{r message = FALSE, warning = FALSE}
walk2(p_list,names,transform)
```

That's alot of numbers. At any rate, here are the best ones.`time at doctors` with a `log`. `Physical health` with `log`. `Mental Health` with `square root` and `mental health` with `square root`
here's some code that adds it into the data file
```{r}
lab3 <- lab3 %>%
  mutate(timedrs_log = log10(timedrs+1),
         phyheal_log = log(phyheal+1),
         menheal_sqrt = sqrt(menheal +1),
         stress_sqrt = sqrt(stress +1))
```    

##Q3
cause i'm lazy
```{r message=FALSE, warning=FALSE}
lazy.list <- list(lab3$timedrs,lab3$phyheal,lab3$menheal,lab3$stress,lab3$timedrs_log,lab3$phyheal_log,lab3$menheal_sqrt,lab3$stress_sqrt)
lazy.names <- names(lab3[2:9])
zz<-walk2(lazy.list,lazy.names,skurt)
```
Table.1 Skewness, kurtosis and confidence intervals
-------------------------------------------------------------------------------------
Variable(transformation)|Skewness[confidence interval]|Kurtosis[confidence interval]|  
------------------------|-----------------------------|-----------------------------|
Timedrs                 |3.25[2.64,4.03]              |13.10[8.16,21.32]            | 
Timedrs(log)*           |0.23[0.00,.44]               |-0.18[-0.46,0.29]            | 
phyheal                 |1.03[0.76,1.43]              |1.12[0.10,2.69]              | 
phyheal_log*            |0.16[-0.02,0.35]             |-0.64[-0.89,-0.31]           | 
menheal                 |0.60[0.41,0.84]              |-0.29[-0.69,0.35]            | 
menheal_sqrt*           |-0.02[-0.19,0.14]            |-0.67[-0.89,-0.40]           | 
stress                  |1.04[0.67,1.69]              |1.80[0.08,5.52]              | 
stress_sqrt*            |-0.04[-0.27,0.30]            |0.00[-0.41,0.89]             | 
------------------------------------------------------------------------------------
*fixed problems with skew.

##Q4
### plots
```{r}
par(mfrow = c(2,2))
plot(lab3$phyheal_log, lab3$timedrs_log)
lines(lowess(lab3$phyheal_log, lab3$timedrs_log))
plot(lab3$menheal_sqrt, lab3$timedrs_log)
lines(lowess(lab3$menheal_sqrt, lab3$timedrs_log))
plot(lab3$stress_sqrt, lab3$timedrs_log)
lines(lowess(lab3$stress_sqrt, lab3$timedrs_log))
```

##Q5
###untransformed
```{r}
heal.mod <- lm(timedrs ~ phyheal + menheal + stress, data = lab3)
summary(heal.mod)
par(mfrow = c(2,2))
plot(heal.mod)
vif(heal.mod)
1/vif(heal.mod)
lmtest::bptest(heal.mod, varformula = ~ fitted.values(heal.mod), studentize = FALSE)
```

##Q6
###transformed
Transformed variables are better than the untransformed. Furthermore, the residuals and plots are more evenly distributed. The Breusch-Pagan is not significant which indicates that data is homoscedastic.
```{r}
heal.mod.2 <- lm(timedrs_log ~ phyheal_log  + menheal_sqrt  + stress_sqrt, data = lab3)
summary(heal.mod.2)
par(mfrow = c(2,2))
plot(heal.mod.2)
lmtest::bptest(heal.mod.2, varformula = ~ fitted.values(heal.mod.2), studentize = FALSE)
```

##Q7
Multicolinearity is also not a problem because the variance inflation factor and 1/VIF are low.
```{r}
vif(heal.mod.2)
1/vif(heal.mod.2)
```

##Q8
Multivariate outliers are not a problem because _p_ was not <.001.
```{r}
n <- 465
hat <- hatvalues(heal.mod.2)
mahun<-((n-1)*(hat))-1
tail(sort(mahun),10)
1-pchisq(13.99, df = 3)
```


