---
title: "Lab 6"
author: "Ben Chu"
date: "April 10, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
load("C:/Users/Branly Mclanbry/Downloads/lab6.RData")
```

cleaning data
```{r}
lab <- lab6 %>%
  separate(date_, c("month.factor","year1"), sep = " ") %>%
  mutate(law.numeric = as.numeric(lawprepo))
```

#1
```{r}
b <- ggplot(lab,aes(x=fct_inorder(month.factor),y = arrests))
b+stat_summary(fun.y=mean,geom="bar",position="dodge")
```

  I'm not going to lie, it looks like there are more arrests happening from April to August, this is probably because ice cream sales are going up and apparently there is a correlation between ice cream sales and crime. 
  
#2
```{r}
b <- ggplot(lab,aes(x=(time),y = arr_adj))
b+stat_summary(fun.y=mean,geom="bar",position="dodge")
```  

Yes, Yes there does seem to be a reduction in arrests at that point.

#3
```{r}
mod <- lm(arr_adj~law.numeric,lab)
summary(mod)
```
##a Some durbins
There is not a autocorrelation so the assumptions are not met.
```{r}
lmtest::dwtest(mod)
```
##b Some Pankrantz
There are a series of lines spiking across the CI, so assumption is not met.
```{r}
acf(residuals(mod), ci = .79, ylab="1.25 ACF/SE criteria")
acf(residuals(mod), ci = .89, ylab="1.60 ACF/SE criteria")
```

##c Some BoxLjuns
These are just significant at the 1 lag.
```{r}
Box.test(residuals(mod), lag = 1, type = c("Ljung-Box"))
Box.test(residuals(mod), lag = 2, type = c("Ljung-Box"))
Box.test(residuals(mod), lag = 3, type = c("Ljung-Box"))
Box.test(residuals(mod), lag = 4, type = c("Ljung-Box"))
```

##d
Quite Frankly, a LM is not appropriate to use.

#4
```{r}
library(forecast)
fit.1 <- Arima(lab$arr_adj,lab$law.numeric,order=c(19,0,0))
fit.3 <- Arima(lab$arr_adj,lab$law.numeric,order=c(3,0,0))
fit.2 <- Arima(lab$arr_adj,lab$law.numeric,order=c(2,0,0))
acf(residuals(fit.1, ci=.79,ylab="1.25 ACF/SE criteria"))
acf(residuals(fit.1, ci=.89,ylab="1.60 ACF/SE criteria"))
```

##a
Assumptions
```{r}
acf(residuals(fit.1), ci = .79, ylab="1.25 ACF/SE criteria")
acf(residuals(fit.1), ci = .89, ylab="1.60 ACF/SE criteria")
```
##b
```{r}
Box.test(residuals(fit.1), lag = 1, type = c("Ljung-Box"))
Box.test(residuals(fit.1), lag = 2, type = c("Ljung-Box"))
Box.test(residuals(fit.1), lag = 3, type = c("Ljung-Box"))
Box.test(residuals(fit.1), lag = 4, type = c("Ljung-Box"))
```
##c
19 autoregressions seemed to work.

  
#5
```{r}
summary(fit.1)
test <- fit.1$coef/sqrt(diag(fit.1$var.coef))
(1-pnorm(abs(fit.1$coef)/sqrt(diag(fit.1$var.coef))))*2
```
There was a significant decrease in arrests after a new law was instituted _b_ = 3.26, _p_ < .05

